What's in a Domain?

### 2022-09-16 paper/paper.tex
Reshaping paper template

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Evaluating Ad Creative and Web Context Alignment with Attention Measurement}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{John Hawkins}
\email{john.hawkins@playgroundxyz.com}
\orcid{1234-5678-9012}
\author{Graham Burton}
\email{graham.burton@playgroundxyz.com}
\affiliation{%
  \institution{Playground XYZ}
  \streetaddress{Level 11/61 York St}
  \city{Sydney}
  \state{NSW}
  \country{Australian}
  \postcode{2000}
}

\renewcommand{\shortauthors}{Hawkins \& Burton}

\begin{abstract}
Contextual targeting is a common strategy that places marketing messages
in media locations that are aligned with a target audience.
The challenge of contextual targeting is knowing the ideal schema and
the set of categories that provide the right audience.
Refinement of the contextual targeting process has been
limited by the use of metrics that are either rapid but
unreliable (click through rates), or reliable
but slow, expensive and inaccessible in real-time (conversions or brand awareness).

In this study we evaluate the use of attention measurement as a technique for
understanding the alignment between advertising creatives and media contexts.
We perform the analysis using
a large scale dataset of impressions categorised using the iAB V2.0 taxonomy. We
evaluate the alignment by looking for consistency across time in the attention
a given creative attracts over the levels of the categorisation hierarchy.

Our research is the largest known study of the relationship between advertising creative,
media context and consumer attention. We provide strong empirical evidence that consumer
attention is related to an alignment between the creative execution and topics of media
context. Furthermore, we show that this relationship transcends any specific publication
by providing reliable indications of attention on new website domains.

@@

\keywords{Contextual Targeting, Attention Measurement, Digital Advertising, Digital Media}

@@

\section{Introduction}
Contextual targeting allows advertisers to reach people with known interests,
rendered explicit
by the choice to consume media with content about a specific topic.
These contexts are thereby used to infer potential purchase intentions,
due to the association
between interests and products. Context is increasingly seen as a critical
factor in creating and defining brand engagement \cite{Wang2006}.

Context is also often used as an indirect method of reaching people that belong to certain
audiences or groups on the basis that people's interests and demographics are aligned \cite{str2016}.
A strategy that may be more effective given that targeting on the basis of gender alone
may not drive better results for many campaigns \cite{Jansen2013}.
The underlying assumptions about the relationships between demographics,
content and intentions
are supported by investigations into the social media behaviour of different demographic
groups \cite{Wang2016}.
Multiple studies have looked at the effect of media context on advertising outcomes.
A recent meta-analysis found significant effects for multiple dimensions of
media context on advertising recall \cite{Kwon2019}.
However, studies that look at the congruence
between the topic context of a page and the content of an ad have found some
counterintuitive results. For
example, brand recall can be associated with ads appearing within irrelevant contexts,
potentially due to an ability to stand out from a suite of relevant ads \cite{Kononova2020}.

The difficulty of implementing effective contextual targeting comes down three key issues.
You will need to determine an ideal contextual hierarcy or categorisation scheme that can be
applied uniformly across all media. You need to identify which components of that categorisation
scheme are appropriate for your brand or specific campaign. Finally, you need to balance the
contextual targeting against other goals like reach and frequency.
Advertisers generally must expand targeting to across high-level categories in order to
fulfill requirements as highly specific contexts are both expensive and rare.

In this work we experiment with the use of gaze duration as a measurement of
visual attention to determine the relative performance of categories within
the iAB V2.0 Contextual Hierarchy \cite{iabv2}.
We undertake this to understand the uniformity of the right context for a given brand, and
the reliability of performance across the hierarchy and across time. The goal is to determine
strategies by which contextual targeting can be refined for advertising outcomes.

Eye tracking studies are widely used as a method of measuring overt attention
to visual stimuli and have been applied to study the extent to which people
look at, and remember, advertising \cite{Hervet2011}. The technology has also
allowed the study of many factors that contribute to effective marketing,
including the impact of images of faces \cite{Djamasbi2010},
the use of animation \cite{Hamborg2012,Lee2012}, the relationship with
social media posts \cite{Barreto2013}, and emotional responses to visual stimuli
in different physical spaces \cite{Kim2021}.

Multiple investigations have identifed that attention time on advertising
provides a real-time metric that is correlated with important downstream
impacts like brand recall \cite{Lee2012}, consideration and purchase intent (\citeauthor{dentsu,PlaygroundXYZ}). Importantly, even though low attention can drive brand outcomes,
multiple studies have demonstrated that greater attention through direct
fixation has a greater impact on marketing outcomes, including
consideration, choice \cite{Santoso2021} and short term advertising
strength \cite{NelsonField}. The pervasive evidence of the role of visual attention
in the success of advertising has led to increasing focus on Attention Based Marketing
research \cite{Orquin2020}.

Contextual relevance is a method of aligning the message in advertising with the editorial
content that it is presented with \cite{Wang2011}. This is not simply a matter of
being \emph{about} the same topic, as consumers's have been shown to
to pay more attention to advertising that is relevant to their current task
(i.e. what they are looking for, or why they are reading) than simply advertising that
is contextually aligned \cite{Resnick2016}. This is coherent with observations
in the psychological literature that overt visual attention is influenced by motivations
and personality traits of individuals \cite{Kaspar2011}. Thus, the role of contextual
targeting may be to bring \emph{top-down} attention selection to advertising that would
otherwise garner attention in a \emph{bottom-up} manner \cite{Greenberg2013}.

We draw on two observations to motivate the current work. Firstly, advertisers are aware
that alignment between a campaign creative and media context can drive outcomes.
Secondly, they require methods for detecting when that alignment is functioning and
when it is not. The thesis of this research is that large scale real-time
measurement of ad attention can determine if an ad is aligned with a specific context,
and thereby provide a tool for fine tuning contextual targeting
strategies for advertiser outcomes. Conversely, it opens the door to using contextual
targeting as a method for advertisers to combat diminishing attention on
advertising \cite{Teixeira2014,Orquin2020}.

@@

In this research we investigate the efficacy of contextual targeting strategies
for obtaining improvements in the mean attention time paid to digital advertising.
The essential research question is whether the attention as ad attracts
within a given media context provides information about its future performance.
The null model assumes that context is not relevant and any contextual
variation should be subject to a regression to the mean.
In other words, the control hypothesis is that the mean attention paid to
a specific creative should be a better predictor of
future attention, than the attention that was paid within a specific context.

For the purposes of obtaining large scale measurements of attention time on
display advertising we utilise a machine learning system trained on data
collected from eye-tracking studies.
The attention model provides an impression level estimate of attention time,
that aggregates up into low error measurements of mean attention
time over groups of inventory.

\subsection{Attention Measurement}

We developed an attention measurement system that predicts attention time from user
behavioural signals. The training data is collected from eye tracking panels in
which subjects read media in self-directed sessions while eye tracking data is collected
using a gaze fixation model trained on facial images \cite{Krafka2016}.

As the eye tracking data is collected, we track a large number of other signals
about the user experience including environmental signals like the page structure,
and behavioural data like scroll events and the position of the advertising
in the viewport.

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{What's in a Domain?}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{John Hawkins}
\email{john.hawkins@Getting-Data-Science-Done.com}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Getting-Data-Science-Done.com}
  \city{Sydney}
  \state{NSW}
  \country{Australia}
  \postcode{2000}
}

\renewcommand{\shortauthors}{Hawkins}

\begin{abstract}

@@

\keywords{URL Features, Document Classification, Machine Learning, Semantic Web}

@@

\section{Introduction}

@@
